A Review on Multi-Label Learning Algorithms

### 2018-01-13 Paper/Presentation/mll_review.tex
update presentation

\begin{frame}
\frametitle{Calibrated Label Ranking}
\begin{itemize}
	\item Second-order approach algorithm
	\item Transform the problem into a label ranking problem
	\item Ranking implemented by pairwise comparison techniques
	\item For $q$ labels, generate $q(q-1)/2$ binary classifiers by pairwise comparison
	\item Construct training set per label pairs considering the example's relevance
	\item For unknown instance, get the overall classifiers' votes
	\item Virtual label $y_v$ as thresholding parameter
\end{itemize}
Pros \& cons:
\begin{itemize}
	\item Smooth the class-imbalance
	\item Classifier's number grows from linear to quadratic scale
	\begin{itemize}
		\item Improvement: Exact or approximate pruning to reduce classifier's number to be queried
	\end{itemize}
\end{itemize}
\end{frame}
%------------------------------------------------
\begin{frame}
\frametitle{Random k-Labelsets}
\begin{itemize}
	\item High-order approach algorithm
	\item Decompose to an ensemble of multi-class classification problems
	\item Each component targets a random subset of $Y$, inducing a multi-class classifier by Label Powerset (LP) techniques
	\item Convert training set into a multi-class set, treating each label set as a new class
	\item Each example is reassigned with the mapped single-label participating in multi-class classifier induction
	\item For unknown $x$, counts the maximum and actual number of votes
	\item Label set is relevant when the actual number of votes exceeds
half of the maximum ones
\end{itemize}
Pros \& cons:
\begin{itemize}
	\item Incompleteness: predicts only label sets included in the training set
	\item Inefficiency: large $Y$ implies high training complexity.Improvement by combining LP and ensemble learning
\end{itemize}
\end{frame}
%------------------------------------------------
\subsection{Alogrithm Adaptation Methods}
%------------------------------------------------
\begin{frame}
\Huge{\centerline{Alogrithm Adaptation Methods}}
\end{frame}
%------------------------------------------------
\begin{frame}
\frametitle{Multi-Label k-Nearest Neighbour}
\begin{itemize}
	\item First-order approach algorithm, adapting knn techniques
	\item Maximum a posteriori (MAP) rule to make prediction by reasoning and embody label info in the neighbours
	\item For new instances, $N(x)$ represents the set of its knn (uses Euclidean distance)

@@

%------------------------------------------------
\begin{frame}
\frametitle{Multi-label Decision Tree}

\end{frame}
%------------------------------------------------
\begin{frame}
\frametitle{Ranking Support Vector Machine}

\end{frame}
%------------------------------------------------
\begin{frame}
\frametitle{Collective Multi-Label Classifier}

\end{frame}
%------------------------------------------------
\section{Related Learning Settings}
%------------------------------------------------

\begin{frame}
\frametitle{Related Learning Settings}
\begin{itemize}
\item 
\item 
\item 
\item 
\end{itemize}
\end{frame}

%------------------------------------------------
\section{Conclusion}
%------------------------------------------------
\begin{frame}
\frametitle{Conclusion}
\begin{itemize}
	\item 
\end{itemize}
\end{frame}

>>>>

\begin{frame}
\frametitle{Calibrated Label Ranking}
\begin{itemize}
	\item Second-order approach algorithm
	\item Transform the problem into a label ranking problem
	\item Ranking implemented by pairwise comparison techniques
	\item For $q$ labels, generate $q(q-1)/2$ binary classifiers by pairwise comparison
	\item Construct training set per label pairs considering the example's relevance
	\item For unknown instance, get the overall classifiers' votes
	\item Virtual label $y_v$ as artificial splitting point between relevant and irrelevant labels
\end{itemize}
Pros \& cons:
\begin{itemize}
	\item Smooth the class-imbalance
	\item Classifier's number grows from linear to quadratic scale
	\begin{itemize}
		\item Improvement: Exact or approximate pruning to reduce classifier's number to be queried
	\end{itemize}
\end{itemize}
\end{frame}
%------------------------------------------------
\begin{frame}
\frametitle{Random k-Labelsets}
\begin{itemize}
	\item High-order approach algorithm
	\item Decompose to an ensemble of multi-class classification problems
	\item Each component targets a random subset of $Y$, inducing a multi-class classifier by Label Powerset (LP) techniques
	\item Convert training set into a multi-class set, treating each label set as a new class
	\item Each example is reassigned with the mapped single-label participating in multi-class classifier induction
	\item For unknown $x$, counts the maximum and actual number of votes
	\item Label set is relevant when the actual number of votes exceeds
half of the maximum ones
\end{itemize}
Pros \& cons:
\begin{itemize}
	\item Incompleteness: predicts only label sets included in the training set
	\item Inefficiency: large $Y$ implies high training complexity.Improve by invoking LP only on random k-labelsets and ensemble learning to LP classifiers
\end{itemize}
\end{frame}
%------------------------------------------------
\subsection{Alogrithm Adaptation Methods}
%------------------------------------------------
\begin{frame}
\Huge{\centerline{Algorithm Adaptation Methods}}
\end{frame}
%------------------------------------------------
\begin{frame}
\frametitle{Multi-Label k-Nearest Neighbour}
\begin{itemize}
	\item First-order approach algorithm, adapting knn techniques
	\item Lazy learning and Bayesian reasoning
	\item Maximum a posteriori (MAP) rule to make prediction by reasoning and embody label info in the neighbours
	\item For new instances, $N(x)$ represents the set of its knn (uses Euclidean distance)
	\item Posterior probability $\mathbb{P}(H_j|C_j)$ and $\mathbb{P}(\neg H_j|C_j)$, where $C_j$ is the knn of $x$ and $H_j$ is the event that $x$ has the label $y_j$
	\item Predict relevant label set based on which probability is higher(MAP rule)
	\item Frequency counting strategy:
	\begin{enumerate}
		\item Estimation of prior probabilities ($\mathbb{P}(H_j)$ \& $\mathbb{P}(\neg H_j)$) using a smoothing parameter $s$ (usually $s=1$)
		\item Estimation of likelyhoods (($\mathbb{P}(C_j|H_j)$ \& $\mathbb{P}(C_j|\neg H_j)$)
	\end{enumerate}

@@

%------------------------------------------------
\begin{frame}
\frametitle{Multi-label Decision Tree}
\begin{itemize}
	\item First-order approach algorithm, that adopts decision tree techniques
	\item ML entropy is used to
build the decision tree recursively
	\item ML dataset $T$ is divided based on a splitting value $\theta$ ($T^-$ \& $T^+$)
	\item Starting from the root, ML-DT identifies the feature and the splitting value which
maximizes the information gain and creates the two child nodes
	\item ML-DT assumes independence among labels and computes the ML
entropy in a decomposable way
	\item Any test instance allocated in a leaf node is associated with the most frequent label $y$ present in that node
\end{itemize}
Pros \& cons:
\begin{itemize}
	\item High efficiency
	\item Improvement: pruning strategy  or ensemble learning techniques
\end{itemize}
\end{frame}
%------------------------------------------------
\begin{frame}
\frametitle{Ranking Support Vector Machine}
\begin{itemize}
	\item Second-order approach algorithm, that adopts maximum margin strategy 
	\item $q$ linear classifiers, optimized to minimize the empirical
ranking loss and enabled to handle nonlinear cases with kernel tricks 
	\item $W = {(w_j , b_j ) | 1 ≤ j ≤ q}$,where $w_j \in \mathbb{R}^d$ and
$b_j \in \mathbb{R}$ are the weight vector and bias
	\item Rank-SVM defines the learning system's
margin on ($x_i$ , $Y_i$), considering its ranking ability on the example’s relevant/irrelevant labels
\end{itemize}
\end{frame}
%------------------------------------------------
\begin{frame}
\frametitle{Collective Multi-Label Classifier}
\begin{itemize}
	\item 
	\item 
	\item 
	\item 
\end{itemize}
\end{frame}
%------------------------------------------------
\section{Related Learning Settings}
%------------------------------------------------

\begin{frame}
\frametitle{\insertsection}
\begin{itemize}
	\item 
	\item 
	\item 
	\item 
\end{itemize}
\end{frame}

%------------------------------------------------
\section{Conclusion}
%------------------------------------------------
\begin{frame}
\frametitle{\insertsection}
\begin{itemize}
	\item 
\end{itemize}
\end{frame}
